---
title: "Assignment"
author: "Rachel Nunley"
date: "2023-08-16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(habtools)
library(ggplot2)
library(dplyr)
library(fishualize)
plot(horseshoe)
```

### Current lab
ToBo Lab

### Project focus
Sponge Taxonomy

### Why you chose this course
This course will give me a better understanding of coral reefs in general and hopefully I'm able to apply this to my sponge research.

### What do you want to learn about the most in this course
I hope to be more proficient in R but also learn more about reef structure and function so I can better understand the roles sponges play in this ecosystem.

### Your R experience
I took MBIO 612 with Mahdi, I also took ZOOL 780/781 which required a heavy use of R related to population changes and other ecological/evolutionary concepts. I'm not great at R, but I have beginner-intermediate experience.

### Fun fact
I have a cat, his name is Winston. We like to go on walks together.